---
title: "nirbdoms"
author: "Zofia Tillman"
date: "`r Sys.Date()`"
output:
  github_document:
    html_preview: false
---

Data and code used to run analysis and create visualizations/tables for 'Rapid monitoring of fermentations – a feasibility study on biological 2,3-butanediol production' (Biotechnology for Biofuels and Bioproducts 2025)

## How to Reproduce Analysis

1. Clone Repository

2. Download the research data used to perform this analysis from data.nrel.gov - Data for "Rapid monitoring of fermentations- a feasibility study of biological 2,3-butanediol production" and save data to data/raw folder within repository

3. Produce Models by working through the following scripts: 

  * laboratoryatline_full_modelbuild.R (lab grade full models)
  * laboratoryatline_lowcostfeasibility_modelbuild.R (lab grade low cost feasibility models)
  * laboratoryatline_onlinefeasibility_modelbuild.R (lab grade on line feasibility models)
  * lowcostatline_modelbuild.R (low cost at line models)
  * laboratoryonline_modelbuild.R (laboratory grade on line models)
  
4. Produce Figures and Tables describing the models by working through the following scripts: 

  * figure_(1-S11).R  code used to generate each figure in the manuscript
  * table_(S1-5).R code used to generate each table in the manuscript

```{r library_calls, message=FALSE, echo=FALSE, warning = FALSE}
library(tidyverse)
library(pls)
library(prospectr)
library(ggpmisc)
library(openxlsx)
library(egg)
library(ggsci)
library(caret)
library(ggtext)
library(GGally)
library(patchwork)
library(Hmisc)
```

## Dependencies

* `r R.version.string`
  * `tidyverse` (v. `r packageVersion("tidyverse")`)
  * `pls` (v. `r packageVersion("pls")`)
  * `prospectr` (v. `r packageVersion("prospectr")`)
  * `ggpmisc` (v. `r packageVersion("ggpmisc")`)
  * `openxlsx` (v. `r packageVersion("openxlsx")`)
  * `egg` (v. `r packageVersion("egg")`)
  * `ggsci` (v. `r packageVersion("ggsci")`)
  * `caret` (v. `r packageVersion("caret")`)
  * `ggtext` (v. `r packageVersion("ggtext")`)
  * `GGally` (v. `r packageVersion("GGally")`)
  * `patchwork` (v. `r packageVersion("patchwork")`)
  * `Hmisc` (v. `r packageVersion("Hmisc")`)
  * `rmarkdown` (v. `r packageVersion("rmarkdown")`)
  

## My Computer

```{r sessioninfo, echo=FALSE}
sessionInfo()
```